An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-02 scagnostics.Rmd
Section on data standardization?

@@

Focusing now on $n=2$ dimensional projections, we aim to identify projections that reveal interesting structures or correlations between combinations of variables. We therefore draw on index functions that have been developped for the selection of variable pairs that show interesting features in a scatter plot, but we generalise the notion such that instead of variable pairs we consider any $2$ dimensional projection of the multivariate data distribution. It means that we consider the projection axes as input to the index functions, which will thus score the interestingness of the given projection.
Concretely here we consider the following types of index functions:

>>>>

## Standardization
scaling/sphering of data? what about outlier removal? it is build in for calculation of scagnostics measures, but not the other index functions, can generate "fake linear behaviour" by highlighting direction with outliers
consider using log transformed parameter as appropriate? e.g. timeseries examples...

@@

Focusing now on $n=2$ dimensional projections, we aim to identify projections that reveal interesting structures or correlations between combinations of variables. We therefore draw on index functions that have been developped for the selection of variable pairs that show interesting features in a scatter plot, but we generalise the notion such that instead of variable pairs we consider any $2$ dimensional projection of the multivariate data distribution. It means that we consider the projection axes as input to the index functions, which will thus score the interestingness of the given projection. What we are optimising over are then the entries of the $p\times2$ dimensional projection matrix, considering that they obey orthonormality conditions.
Concretely here we consider the following types of index functions (give definitions in Appendix??):
